---
title: "OnTrack Pre-Curated: Investigate Raw MDA Data"
author: "Tony Banks"
date: '2022-07-18'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(haven)
library(dplyr)
library(stringr)
library(data.table)
library(openxlsx)
library(tidyr)
library(lubridate)
library(purrr)
library(gtools)
library(scales)
library(readxl)
library(knitr)
library(kableExtra)
library(DT)
library(Hmisc)
library(haven)

source("../paths.R")

prefix_func <- function(colname, prefix){
  if(colname %in% c("Grafana.UserName", "PPT.ID", "SubjectID", "ses_integer", "cc_indicator", "ContactID", "ID_enrolled", "participant_id")){
    return(colname)
  } else {
    return(paste(prefix, colname, sep = "_"))
  }
}

mydt <- function(...){datatable(...,rownames=F, extensions = 'Buttons', options = list(lengthMenu = c(10,20,50,100,200),
                                                                                       autoWidth=T,
    dom = 'lBrtip',
    buttons = list(list(extend = 'colvis'),"copy","csv")
  ),
            filter = list(
  position = 'top', clear = FALSE
            ))}

```

# Prep Data Sources from MDA

## Excel Tracker - used by study staff
```{r}
tracker <- read.xlsx(file.path(path_ontrack_visit_inputs, "Grafana Accts submitted to Utah by ALG- Coordinator USE ONLY 01.14.2022.xlsx"))

tracker_v2 <- tracker 
# add prefix to all unique variables
colnames(tracker_v2) <- colnames(tracker) %>% map(function(.) prefix_func(., "tracker"))

# create a cleaned v1 and v4 date
tracker_v3 <- tracker_v2 %>% 
  mutate(ses_integer = as.integer(str_split(str_remove(Grafana.UserName, "ses_"), " ", simplify = T)[,1]),
         .before = Grafana.UserName) %>% 
  mutate(in_tracker = T) %>% 
  mutate(tracker_date_v1 = ymd(str_remove(tracker_V1_YYYYMMDD, pattern = "V1_")),
         tracker_date_v4 = ymd(str_remove(tracker_V4_YYYYMMDD, pattern = "V4_")),
         .after = tracker_V4_YYYYMMDD) %>% 
  rename(SubjectID = PPT.ID)


# add a comment to supplement an NA date - can also use the comments tracker_Comments variable
tracker_v4 <- tracker_v3 %>% 
  mutate(
    tracker_date_v1_comment = case_when(
      is.na(tracker_date_v1) ~ str_remove(tracker_V1_YYYYMMDD, "V1_")
    ), .after = tracker_date_v1) %>% 
  mutate(
    tracker_date_v4_comment = case_when(
      is.na(tracker_date_v4) ~ str_remove(tracker_V4_YYYYMMDD, "V4_")
    ), .after = tracker_date_v4)

tracker_v5 <- tracker_v4 %>% filter(!is.na(SubjectID)) %>% select(-tracker_Password)

tracker_v6 <- tracker_v5 %>% 
  rename(ID_enrolled = Grafana.UserName,
         participant_id = ses_integer) %>% 
  mutate(participant_id = paste0("ses_", participant_id))

tracker_clean <- tracker_v6

remove(tracker, tracker_v2, tracker_v3, tracker_v4, tracker_v5, tracker_v6)

```

## EMA Subfolders
```{r}
ema_subfolder_names_all <- list.files(path_ontrack_cc2_input_data)
# remove files (retain only folders) and remove folders for test participants
subset_indices <- replace_na(str_split_fixed(ema_subfolder_names_all, "_", n = 2)[,1] == "ses" & !str_detect(ema_subfolder_names_all, "_test_"))
ema_subfolder_names <- ema_subfolder_names_all[subset_indices]

ema_folders_clean <- data.frame(#ses_integer = as.integer(str_remove(ema_subfolder_names, "ses_")), 
                                participant_id = ema_subfolder_names, in_ema_folders = T) 

remove(ema_subfolder_names_all, subset_indices, ema_subfolder_names)
```




## MDA SAS Files

* Previously converted the SAS files to a list of tibbles
```{r}
list_of_MDA_sas_files <- readRDS(file.path(path_ontrack_visit_staged, "list_of_all_sas_data_from_MDA.Rds"))

MDA_sas_files_summary_df <- data.frame(index = integer(), name = character(), n_rows = integer(), n_cols = integer())
for (i in 1:length(list_of_MDA_sas_files)){
  #print(paste0("Index: ",i, ". Name: ", names(list_of_MDA_sas_files[i]), ". Rows: ", dim(list_of_MDA_sas_files[[i]])[1], ". Cols: ", dim(list_of_MDA_sas_files[[i]])[2]))
  MDA_sas_files_summary_df <- MDA_sas_files_summary_df %>% add_row(index = i, name = names(list_of_MDA_sas_files[i]), n_rows = dim(list_of_MDA_sas_files[[i]])[1], n_cols = dim(list_of_MDA_sas_files[[i]])[2])
}
remove(i)
MDA_sas_files_summary_df <- MDA_sas_files_summary_df %>% arrange(desc(n_rows))
```

#### Event
```{r}
event <- list_of_MDA_sas_files[["tblevents"]] %>% relocate(SubjectID, .before = everything())

all(event$EventDate == event$EventTime)

# remove variables that are redundant, NA / same value for all rows, or not likely useful to carryforward
event_clean <- event %>% 
  select(-EventTime, -EventSecondary, -OldEventID, -ContactGroupId, -NextTryDate, -Project, -StaffID, -ActualDate, -VisitType, -EnteredBy, -UniqueIdent) %>% 
  mutate(SubjectID = as.character(SubjectID))

event_clean_wlabels <- event_clean %>% 
  left_join(y = list_of_MDA_sas_files[["rtbleventstatus"]],
            by = c("EventStatusID" = "EventStatusId")) %>% 
  relocate(EventStatus, .after = EventStatusID) %>% 
  left_join(y = list_of_MDA_sas_files[["rtblcontacttype"]],
            by = c("ContactTypeId")) %>% 
  relocate(ContactType, .after = ContactTypeId) %>% 
  select(-EventStatusID, -ContactTypeId, -Status)


event_clean_wide <- event_clean_wlabels %>% 
  arrange(EventNo) %>% 
  pivot_wider(
    id_cols = SubjectID,
    names_from = EventNo,
    names_glue = "event_v{EventNo}_{.value}",
    values_from = colnames(event_clean_wlabels)[!colnames(event_clean_wlabels) %in% c("SubjectID", "EventNo")]
  ) %>% 
  mutate(in_event = T) 

remove(event, event_clean)
```

#### Subject Status
```{r}
status <- list_of_MDA_sas_files[["tblsubjectstatus"]] %>% relocate(SubjectID, .before = everything())

colnames(status) <- colnames(status) %>% map(function(.) prefix_func(., "status"))

status <- status %>% 
  mutate(SubjectID = as.character(SubjectID), 
         in_subjectstatus = TRUE)

if(T){status %>% count(status_StudyStatus, status_SecondaryStatus)}

crswlk <- status %>% select(SubjectID, ContactID)
```

```{r}
progressnotes <- crswlk %>% 
  full_join(y = list_of_MDA_sas_files[["tblprogressnotes"]],
            by = c("ContactID")) %>% 
  arrange(SubjectID, EventNo, NoteDate)

```

#### Randomization
```{r}
randomization <- list_of_MDA_sas_files[["tblrandomization"]]
randomization_clean <- randomization %>% 
  select(-Name, -Method, -ActiveRandom, -CreateBy) %>% 
  rename(SubjectID = SubjectId) %>% 
  mutate(SubjectID = as.character(SubjectID))

colnames(randomization_clean) <- colnames(randomization_clean) %>% map(function(.) prefix_func(., "rand"))

randomization_clean <- randomization_clean %>% mutate(in_rand = T)

remove(randomization)
```

## Load the EMA first and last dates
```{r}
ema_first_last_dates <- readRDS(file = file.path(path_ontrack_visit_staged, "ema_first_last_dates.rds")) %>% 
  filter(cc_indicator == "2") #%>% 
  #rename(Grafana.UserName = participant_id) %>% 
  #mutate(ses_integer = as.integer(str_remove(Grafana.UserName, "ses_")), .after = Grafana.UserName) %>% 
  #arrange(ses_integer) 

colnames(ema_first_last_dates) <- colnames(ema_first_last_dates) %>% map(function(.) prefix_func(., "ema_dates"))

ema_first_last_dates <- ema_first_last_dates %>% 
  mutate(in_ematimes = TRUE)

```

#### Questionairre
```{r}
#quest <- read.xlsx(file.path(path_ontrack_mda_raw, "OnTrack_Qualtrics_2022_08_30.xlsx"))
quest_raw <- read.xlsx(file.path(path_ontrack_mda_raw, "OnTrack_Qualtrics_2022_08_30_clean.xlsx")) 

colnames(quest_raw) = make.names(colnames(quest_raw), unique = T)

quest_raw <- quest_raw %>% select(-StartDate_orig, -EndDate_orig, -RecordedDate_orig)

quest_labels <- quest_raw[1,]
quest <- quest_raw[2:nrow(quest_raw),] %>% 
  mutate(across(.cols = c(StartDate, EndDate, RecordedDate), .fns = lubridate::mdy_hms))

remove(quest_raw)


quest %>%
    dplyr::group_by(SubjectID_, Visit_) %>%
    dplyr::summarise(StartDate, Finished, n_total = dplyr::n(), .groups = "drop") %>%
    dplyr::filter(n_total > 1L)


# 18 cases of repeated questionnaire per event per participant. Mixed completion results. Algorithm below reduces to max 1 per participant. Max 2 observed
quest_dates <- quest %>% 
  arrange(StartDate) %>% 
  group_by(SubjectID_, Visit_) %>% 
  mutate(keep_from_dup = case_when(
    n() == 1 ~ TRUE,  # If not repeated, then keep the entry
    row_number() == n() & Finished == "TRUE" ~ TRUE, # If multiple, and the chronologically last was completed, use that one
    row_number() == n() & Finished != "TRUE" & any(Finished == "TRUE") ~ FALSE, # If multiple, and the chronologically last was not completed, but the other was, then don't keep the chronologically last one
    row_number() != n() & Finished == "TRUE" & !all(Finished == "TRUE") ~ TRUE, # If multiple, and the chronologically last was not completed, but the other was, then keep the other
    row_number() == n() & Finished != "TRUE" & !any(Finished == "TRUE") ~ TRUE, # If multiple and none completed, keep the chronologically last. 
    #Could modify for the most complete!
    row_number() != n() & Finished != "TRUE" & !any(Finished == "TRUE") ~ FALSE, # Opposite of the above
    T ~ FALSE
  )) %>% 
  filter(keep_from_dup) %>% 
  ungroup() %>% 
  arrange(Visit_) %>% 
  pivot_wider(
    id_cols = SubjectID_,
    names_from = Visit_,
    names_glue = "{Visit_}_{.value}",
    values_from = c(EndDate, Finished)
  ) %>% 
  rename(SubjectID = SubjectID_) 

colnames(quest_dates) <- colnames(quest_dates) %>% map(function(.) prefix_func(., "quest"))

quest_dates <- quest_dates %>% 
  mutate(in_quest = T)

```


## Demographics
```{r}
demog <- list_of_MDA_sas_files[["tbldemographics"]] %>% rename(SubjectID = subjectid) %>% mutate(SubjectID = as.character(SubjectID))

colnames(demog) <- colnames(demog) %>% map(function(.) prefix_func(., "demog"))
```




## MDA Withdraw Log
```{r}
withdraw_log <- read_excel(path = file.path(path_ontrack_mda_raw, "withdraw log_clean.xlsx")) %>% 
  mutate(withdrawn_date = mdy(str_remove(Withdrawn_date_text, 'withdrew on ')),
         Subject_ID = as.character(Subject_ID)) %>% select(Subject_ID, withdrawn_date)


```






## Combine the above 
```{r}
data_all <- status %>% 
  full_join(y = randomization_clean,
            by = c("SubjectID")) %>% 
  full_join(y = event_clean_wide,
            by = c("SubjectID")) %>% 
  full_join(y = tracker_clean, 
            by = c("SubjectID")) %>% 
  full_join(y = ema_first_last_dates,
            by = "participant_id") %>% 
  full_join(y = demog,
            by= c("SubjectID")) %>% 
  full_join(y = quest_dates,
            by = c("SubjectID")) %>%
  full_join(y = withdraw_log %>% mutate(withdrew = T),
            by = c("SubjectID" = "Subject_ID"))%>% 
  mutate(across(where(is.logical), ~replace_na(.,F))) %>%
  mutate(enrolled = status_StudyStatus == "Randomized/Baseline",
         completed_study = case_when(
           enrolled & status_SecondaryStatus == 'Completed Study' ~ T,
           enrolled & status_SecondaryStatus != 'Completed Study' ~ F)
         )  
```



# Reviewing Visit Dates

## Visit 1 (V1)
+ SubjectID 530123: Conflicting v1 dates. The other visit dates from source "Event" coincide with the timeline of event_v1_EventDate, as does the first ema_date. 
  Also, the tracker v4 date coincides with the v4 from "Event". 
  Resolution: use event_v1_EventDate
+ SubjectID 530194: Conflicting v1 dates. The other visit dates from source "Event" coincide with the timeline of event_v1_EventDate, as does the first ema_date. 
  The tracker v4 date does not coincide with the v4 from "Event". Appears the participant's schedule was delayed by 1 week and the tracker was not updated.
  Resolution: use event_v1_EventDate
```{r}

data_all %>% select(ID_enrolled, SubjectID, tracker_date_v1, event_v1_EventDate, ema_dates_hrts_AmericaChicago_first, quest_Baseline_EndDate, event_v1_EventStatus, tracker_date_v1_comment, event_v1_Comments) %>% 
  mutate(event_v1_EventDate = as_date(event_v1_EventDate),
         ema_dates_hrts_AmericaChicago_first = as_date(ema_dates_hrts_AmericaChicago_first)) %>% 
  filter(tracker_date_v1 != event_v1_EventDate)

if(F){
  data_all %>% filter(SubjectID %in% c("530123", "530194")) %>% View()
}

data_all <- data_all %>% 
  mutate(
    v1_date_curated = case_when(
      SubjectID %in% c("530123", "530194") ~ as_date(event_v1_EventDate),
      T ~ as_date(event_v1_EventDate)
      )
    )

```

## Visit 4 (V4)
### Part 1: tracker and event discrepencies
+ SubjectID 530147: tracker_date_v4 lines up with study design timeline, but ema_dates_last coincides with event_v4_EventDate. "tblprogressnotes" indicates the v4 visit occurred on 3/11/2021
  Resolution: Use tracker_date_v4 (3/11/2021)
+ SubjectID 530194: Patient had inconsistent v1 date in tracker as well. 
  Resolution: Use event_v4_EventDate
+ SubjectID 530226: tracker_date_v4 lines up with study design timeline, but ema_dates_last coincides with event_v4_EventDate. "tblprogressnotes" indicates the v4 visit occurred on 6/7/2021
  Resolution: Use event_v4_EventDate (6/7/2021)
```{r}
data_all %>% select(ID_enrolled, SubjectID, v1_date_curated, tracker_date_v4, event_v4_EventDate, ema_dates_hrts_AmericaChicago_last, `quest_Visit 4_EndDate`, event_v4_EventStatus, tracker_date_v4_comment, event_v4_Comments) %>% 
  mutate(v1_date_curated = as_date(v1_date_curated),
         event_v4_EventDate = as_date(event_v4_EventDate),
         ema_dates_hrts_AmericaChicago_last = as_date(ema_dates_hrts_AmericaChicago_last)) %>% 
  filter(tracker_date_v4 != event_v4_EventDate) #| (is.na(tracker_date_v4) & !is.na(event_v4_EventDate))| (!is.na(tracker_date_v4) & is.na(event_v4_EventDate)))



if(F){
  data_all %>% filter(SubjectID %in% c("530147", "530226")) %>% View()
  data_all %>% filter(SubjectID == "530226") %>% View()
  
  
}

data_all <- data_all %>% 
  mutate(
    v4_date_curated = case_when(
      SubjectID == "530226" ~ tracker_date_v4,
      SubjectID %in% c("530147", "530194") ~ as_date(event_v4_EventDate),
      T ~ as_date(event_v4_EventDate)
    )
  )


```

###Part 2:
SubjectID 530058: "tblprogressnotes" documents v4 was a no-show
All others: tracker comments document reason for no v4
Resolution (all): v4_date_curated -> "NA"
```{r}
(inv_v4_p2 <-  data_all %>% select(ID_enrolled, SubjectID, v1_date_curated, tracker_date_v4, event_v4_EventDate, ema_dates_hrts_AmericaChicago_last, tracker_date_v4_comment, event_v4_EventStatus, event_v4_Comments) %>% 
  mutate(v1_date_curated = as_date(v1_date_curated),
         event_v4_EventDate = as_date(event_v4_EventDate),
         ema_dates_hrts_AmericaChicago_last = as_date(ema_dates_hrts_AmericaChicago_last)) %>% 
  filter((is.na(tracker_date_v4) & !is.na(event_v4_EventDate))| (!is.na(tracker_date_v4) & is.na(event_v4_EventDate))) %>% 
   arrange(tracker_date_v4_comment))


data_all <- data_all %>% mutate(
  v4_date_curated = case_when(
    tracker_date_v4_comment %in% c("cancelled", "CANCELLED", "NO SHOW to V4", "NS") ~ NA_Date_,
    T~v4_date_curated
  )
)

(inv_v4_p2B <-  data_all %>% select(ID_enrolled, SubjectID, tracker_date_v4, event_v4_EventDate, ema_dates_hrts_AmericaChicago_last, tracker_Comments, tracker_date_v4_comment, withdrawn_date, event_v4_Comments, v1_date_curated, v4_date_curated) %>% 
  mutate(v1_date_curated = as_date(v1_date_curated),
         event_v4_EventDate = as_date(event_v4_EventDate),
         ema_dates_hrts_AmericaChicago_last = as_date(ema_dates_hrts_AmericaChicago_last)) %>% 
  filter((is.na(tracker_date_v4) & !is.na(event_v4_EventDate))| (!is.na(tracker_date_v4) & is.na(event_v4_EventDate))) %>% 
  filter(!is.na(v4_date_curated)))

data_all <- data_all %>% 
  mutate(v4_date_curated = case_when(
    is.na(tracker_date_v4) & !is.na(event_v4_EventDate) ~ NA_Date_,
    T ~v4_date_curated
  ))

```

## Only count enrolled participants as those who have EMA data and completed the v1 visit

```{r}
data_all <- data_all %>% 
  mutate(
    enrolled = case_when(
      enrolled & !in_ematimes ~ FALSE,       # considered enrolled based on the earlier definition, but don't have EMA data
      enrolled & is.na(v1_date_curated) ~ FALSE,   # considered enrolled based on the earlier definition, but don't have a v1_date_curated
      T ~ enrolled
    )
  )

```


```{r}
# ID_enrolled ses_118 ('530079') was assigned the same grafana account as ses_119 ('530067'). Therefore their data was mingled and could not be parsed. Both will be removed
data_all <- data_all %>% 
  mutate(enrolled = case_when(
    SubjectID %in% c('530067', '530079') ~ FALSE,
    is.na(enrolled) ~ FALSE,
    T ~ enrolled
  ))

```


## Prep outputs
```{r}
data_all <- data_all %>% rename(ID_MDA = SubjectID,
                                cohort = rand_GroupAssigned)

enrolled_mda <- data_all %>% filter(enrolled) %>% mutate(cc_indicator = 2)
data_all_mda <- data_all

dat_master_mda <- enrolled_mda %>% 
  select(ID_MDA, ID_enrolled, participant_id, enrolled, withdrew, v1_date_curated, event_v1_EventStatus, event_v1_ContactType, event_v2_EventDate, event_v2_EventStatus, event_v2_ContactType, event_v3_EventDate, event_v3_EventStatus, event_v3_ContactType, v4_date_curated, event_v4_EventStatus, event_v4_ContactType) 

if(F){dat_master_mda %>% group_by(ID_MDA) %>% summarise(dates_synchronous = v1_date_curated < event_v2_EventDate & event_v2_EventDate < event_v3_EventDate & event_v3_EventDate < v4_date_curated) %>% View}

if(F){dat_master_mda %>% group_by(ID_MDA) %>% summarise(dates_synchronous = v1_date_curated < event_v2_EventDate & event_v2_EventDate < event_v3_EventDate ) %>% View}


saveRDS(data_all_mda,
        file = file.path(path_ontrack_visit_outputs, "data_all_mda.RDS"))

saveRDS(enrolled_mda,
        file = file.path(path_ontrack_visit_outputs, "enrolled_mda.RDS"))
```
